Standalone Tactics using OpenTheory

### 2012-01-15 paper.tex
slight reorganisation, towards rough diamond form

\section{Tactics in Proof Assistants}

@@

@@

\section{\OpenTheory for Tactic Communication}
\label{sec:opentheory}

Introduction to article format.
Representing terms and proofs in the format.
Viewing tactics as derived inference rules.
Implementation details to make standalone.

Implementation details to put on the web.
Examples of tactics for which it is done: HolQbf, HolSmt, HolSat, sledgehammer, TFL, function package, Metis, datatype packages, arithmetic decision procedure.

\section{Performance}
\label{sec:performance}

@@

Evidential tool bus.
System on TPTP.
Natural extension of the integration of automatic tools into interactive systems.

>>>>

OpenTheory is designed for storing and sharing higher-order logic theories.
By using OpenTheory to communicate to tactics (sending goals and receiving proofs), we obtain
\begin{enumerate}
\item
A standard format (article files) for goals and proofs, and
\item
An extensible way to fix the meaning of constants and type definitions.
\end{enumerate}

\subsection{Tactics in Proof Assistants}

@@

Examples of tactics: HolQbf, HolSmt, HolSat, sledgehammer, TFL, function package, Metis, datatype packages, arithmetic decision procedure.

@@

\subsection{\OpenTheory for Tactic Communication}
\label{sec:opentheory}

Introduction to article format.
Representing terms and proofs in the format.
Viewing tactics as derived inference rules.
Implementation details to make standalone.
Implementation details to put on the web.

\section{Preliminary Performance Results}
\label{sec:performance}

@@

Evidential tool bus.
System on TPTP.
Omega.
Natural extension of the integration of automatic tools into interactive systems.
